---
title: "Untitled"
author: "Graham Casey Gibson"
date: "8/20/2020"
output:
  html_document:
    df_print: paged
---


```{r test, warning=FALSE,echo=FALSE, message=FALSE}

## read packages
library(lme4)
library(zoltr) ## devtools::install_github("reichlab/zoltr")
library(tidyverse)
library(lubridate)
## connect to zoltar
zoltar_connection <- new_connection()
zoltar_authenticate(zoltar_connection, "gcgibson", "casey!ili")
## read in fips
fips_csv <- read.csv(url("https://raw.githubusercontent.com/reichlab/covid19-forecast-hub/master/data-locations/locations.csv"))

## access scores for the COVID-19 Forecasts project
tmp <- scores(zoltar_connection, "https://www.zoltardata.com/api/project/44/") %>%
  mutate(wis = (abs_error+.01*interval_2+.025*interval_5+.05*interval_10+.1*interval_20+.15*interval_30+.2*interval_40+.25*interval_50+.3*interval_60+.35*interval_70+.40*interval_80+.45*interval_90)/12,
         mae=abs_error,error=error)

## subset to inc
tmp <- tmp[tmp$target %in% paste0(1:4, " wk ahead inc death"),]
## subset to models of interest
tmp_mech_bayes <- tmp[tmp$model %in%  c("UMass-MechBayes","COVIDhub-baseline"),]
## convert time to date
tmp_mech_bayes$timezero <- as.Date(tmp_mech_bayes$timezero)

## subset to exactly what we want
tmp_subset <- tmp_mech_bayes %>%  dplyr::group_by(timezero,unit,model,target) %>% dplyr::summarize(mae=mean(mae),wis=mean(wis),error=mean(error))

## get geographies MB used
states_ <- unique(tmp_subset[tmp_subset$model == "UMass-MechBayes",]$unit) 
## remove goes we added in July 
states_ <- states_[states_!="US" & states_ != "60" & states_ != "66"&states_ != "69" & states_ != "78" & states_ != "72"]
## subset to common geos
tmp_subset <- tmp_subset[tmp_subset$unit %in% states_,]
## move timezero to V3
tmp_subset <- tmp_subset[tmp_subset$timezero > "2020-05-12",]
## adjust timezero from monday to sunday to be consistent with MB
tmp_subset[tmp_subset$model == "COVIDhub-baseline",]$timezero <- tmp_subset[tmp_subset$model == "COVIDhub-baseline",]$timezero -1
print (head(tmp_subset))
print (nrow(tmp_subset))
```

```{r test2, fig.align='center',warning=FALSE,echo=FALSE, message=FALSE}
mae_results_by_time_zero_df <- tmp_subset[tmp_subset$timezero >= "2020-05-12" & tmp_subset$timezero <= "2020-08-02",] %>% group_by(timezero,model,unit,target) %>% summarize(mae=mean(mae))

mae_results_by_time_zero_df$timezero <- as.factor(mae_results_by_time_zero_df$timezero)
mae_results_by_time_zero <- ggplot(mae_results_by_time_zero_df,aes(x=timezero,y=log(mae),col=model)) + geom_boxplot() + theme_bw() +  theme(axis.text.x = element_text(angle = 90)) 
mae_results_by_time_zero <- mae_results_by_time_zero + geom_hline(yintercept = 0)
print (mae_results_by_time_zero)
```

# Model 1
In order to answer the question of whether there is a stisticaly significant difference between models in terms of MAE, we model log(MAE) as follows

\begin{eqnarray}
log(MAE)_{m,r,t,h}, &=& \beta_0 + \beta_1*\text{model} + \beta_2*\text{2 week ahead} + \beta_3*\text{3 week ahead} + \beta_4*\text{4 week ahead}  \\
&+&  \beta_5*\text{2 week ahead}*\text{model} + \beta_6*\text{3 week ahead}*\text{model} \\
&+& \beta_7*\text{4 week ahead}*\text{model} + \Sigma_{m,r,t,h}
\end{eqnarray}

where $m$ is a model index, $r$ is a geographic index, $t$ is a time index and $h$ is a horizon index. Here we let $\Sigma$ be an auto-regressive covariance matrix of the form, 

\begin{equation}
Cov(log(MAE_{m,r,t_i,h}),log(MAE_{m,r,t_j,h})) = \sigma^2 * \rho^{|t_i-t_j|}
\end{equation}


```{r model 1, message=FALSE}

library(lme4)
library(nlme)
library(pander)
diagnostic_fit <- lme(log(mae + .00001)~ model*target ,random  = ~ 1  + timezero | unit,data=mae_results_by_time_zero_df)
diagnostic_fit <- update(diagnostic_fit, correlation = corAR1())
pander(summary(diagnostic_fit))

```

# Model 2

We can also fit a pure random effects model, with a general covariance structure.

\begin{eqnarray}
log(MAE)_{m,r,t,h}, &=& \beta_0 + \beta_1*\text{model} + \beta_2*\text{2 week ahead} + \beta_3*\text{3 week ahead} + \beta_4*\text{4 week ahead}  \\
&+&  \beta_5*\text{2 week ahead}*\text{model} + \beta_6*\text{3 week ahead}*\text{model}  \\
&+& \beta_7*\text{4 week ahead}*\text{model} +  \beta_8*\text{time} + b_0_r + b_1_r*\text{time} \\
b_0_r &~& N(0,\Sigma_{b_0}^2)\\
b_1_r &~& N(0,\Sigma_{b_1}^2)\\
\end{eqnarray}

```{r model 2, message=FALSE}
diagnostic_fit <- lmer(log(mae+.00001)~ model*target +timezero+  ( 1  + timezero | unit),data=mae_results_by_time_zero_df)

summary(diagnostic_fit)
```



